### 2021-04-14 input/experiments.tex
removing url and doi of biblio + writing text of second experiment

\begin{asparadesc}
\item [Description:] We build a network comprising 10k
  processes. First, we chain processes together, then we add another
  communication link per process to another process. Since links are
  bidirectional, each process has 4 communication links on average. We
  set the latency of links between 20 and 40 ms at random following a
  uniform distribution. We set the weight of links between 5 and 15 at
  random following a uniform distribution. Weights and latency are
  different, hence the first $\alpha$ received by a process may not be
  that of its shortest path. It implies more concurrent operations,
  hence more traffic to reach consistent partitioning.

@@

\noindent We focus on the complexity of \NAME. We measure the average
number of messages generated per process during the experiment; and
the time before reaching consistent partitioning after adding or
removing a partition.

\begin{figure}
  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_complexity.eps}
  \caption{\label{fig:complexity}Overhead of, and time before,
    reaching consistent partitioning using \NAME.}
  %% \caption{\label{fig:complexity}Cumulative average number of messages
  %%   per process in a network comprising 10k processes; along with the
  %%   duration before reaching consistent partitioning after adding or
  %%   removing a partition, totaling 100 new partition then removed.}
\end{figure}

@@

Figure~\ref{fig:complexity} shows the results of this experiment. The
top part of the figure shows the average traffic per process divided
between $\alpha$ and $\delta$ messages. The bottom part of the figure
shows the time before reaching consistent partitioning.

\noindent Figure~\ref{fig:complexity} confirms that \NAME's overhead
depends on the size of partitions. The first partition is the most
expensive, for $\alpha$'s must reach every process which takes time
and generate more traffic. Still, being reactive, as opposed as
cycle-based protocols~\cite{jelasity2007gossip}, \NAME quickly
converge towards consistent partitioning in only 350 milliseconds. The
last and $100^{th}$ partition added around 21 seconds is the least
expensive. By using scoped broadcast, control information only reaches
a small subset of the whole network.

@@

\noindent Figure~\ref{fig:complexity} shows that the overhead of
adding the $1^{st}$ partition does not correspond to the overhead of
deleting this $1^{st}$ partition. When adding it, messages must reach
all processes while when removing it, messages must reach a small
subset of this membership. This is important, for it means that
\NAME's overhead actually depends on the current partitioning, and
does not depend on the past partitioning.

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 adds and the 100 deletes, processes do
not generate traffic anymore. Being reactive, \NAME has no overhead
when there is no operation in the system. This is important, for it
means that \NAME's overhead actually depends on its usage.

@@

\subsection{Distribution and hotspots}

\subsection{Inter-autonomous systems}

>>>>

\begin{asparadesc}
\item [Description:]

We build a network comprising 10k \processes. First, we chain
\processes together, then we add another communication link per
\process to another random \process. Since links are bidirectional,
each \process has 4 communication links on average. We set the latency
of links between 20 and 40 ms at random following a uniform
distribution. We set the weight of links between 5 and 15 at random
following a uniform distribution. Weights and latency are different,
hence the first $\alpha$ received by a \process may not be that of its
shortest path. It implies more concurrent operations, hence more
traffic to reach consistent partitioning.

@@

\noindent We focus on the complexity of \NAME. We measure the average
number of messages generated per \process during the experiment; and
the time before reaching consistent partitioning after adding or
removing a partition.

\begin{figure}
  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_complexity.eps}
  \caption{\label{fig:complexity}Overhead of consistent partitioning
    using \NAME.}
  %% \caption{\label{fig:complexity}Cumulative average number of messages
  %%   per process in a network comprising 10k processes; along with the
  %%   duration before reaching consistent partitioning after adding or
  %%   removing a partition, totaling 100 new partition then removed.}
\end{figure}

@@

Figure~\ref{fig:complexity} shows the results of this experiment. The
top part of the figure shows the average traffic per \process divided
between $\alpha$ and $\delta$ messages. The bottom part of the figure
shows the time before reaching consistent partitioning.

\noindent Figure~\ref{fig:complexity} confirms that \NAME's overhead
depends on the size of partitions. The first partition is the most
expensive, for $\alpha$'s must reach every \process which takes time
and generate more traffic. Still, being reactive, as opposed as
cycle-based protocols~\cite{jelasity2007gossip}, \NAME quickly
converge towards consistent partitioning in only 350 milliseconds. The
last and $100^{th}$ partition added around 21 seconds is the least
expensive. By using scoped broadcast, control information only reaches
a small subset of the whole network.

@@

\noindent Figure~\ref{fig:complexity} shows that the overhead of
adding the $1^{st}$ partition does not correspond to the overhead of
deleting this $1^{st}$ partition. When adding it, messages must reach
all \processes while when removing it, messages must reach a small
subset of this membership. This is important, for it means that
\NAME's overhead actually depends on the current partitioning, and
does not depend on the past partitioning.

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 adds and the 100 deletes, \processes
do not generate traffic anymore. Being reactive, \NAME has no overhead
when there is no operation in the system. This is important, for it
means that \NAME's overhead actually depends on its usage.

@@

%% \subsection{Distribution and hotspots}

% \subsection{Confirm the relevance of \NAME in the context of dynamic inter-autonomous
%   system communications.}
\subsection{Confirm that \NAME locks down the traffic of decentralized content
  indexing in the context of dynamic inter-autonomous system
  communications.}

\begin{figure}
  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_geant.eps}
  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.}
\end{figure}

\begin{asparadesc}
\item [Description:]

We build a network by duplicating the G{\'E}ANT
topology~\cite{knight2011internet} -- a real infrastructure spanning
across Europe -- and by connecting these two clusters with a high
latency link: $200$ ms simulating cross-continental communications
such as Europe-America. The experiments comprise $2 \times 271 = 542$
\processes and we derive intra-cluster latency from their \processes'
geographic location.

\noindent We evaluate the traffic of \NAME by measuring the average
number of messages per \process over the experiments. In the first
experiment, at $50$ ms, only one \process becomes source, hence there
is only one partition for the whole distributed system. In the second
experiment, at $50$ ms, two \processes become sources, one per
cluster. Afterwards both scenarios are identical. At $500$ ms, we
remove the link between the two clusters. At $1200$ ms, we insert this
link again.

Figure~\ref{fig:geant} shows the results of this experimentation. The
top part corresponds to the one source experiment, while the bottom
part corresponds to the one source per cluster experiment.

\noindent Figure~\ref{fig:geant} confirms that concurrent \texttt{Add}
may generate additional traffic, for \processes may deliver and forward
a partition only to later realize that they have a closer source.

\noindent Figure~\ref{fig:geant} highlights that removing the
inter-continental link generates additional traffic. The cluster cut
off the source must remove control information about this source. This
generates $\delta$ messages but also $\alpha$ messages, for \NAME
still triggers competitions in the cut off cluster with $\alpha$
messages that monotonically grows until they are purged off the system
by the anti-looping mechanism and corresponding $\delta$s.  Most
importantly, Figure~\ref{fig:geant} shows that \NAME still operates
as expected when \emph{physical} partitions appear. \Processes from the
cluster without source do not belong to any partition while \processes
from the other cluster belong to the same partition.

\noindent Figure~\ref{fig:geant} shows that, when adding the
inter-continental link again, the two clusters can communicate
again. In the experiment involving one source for two clusters, it
generates traffic. After a $200$ milliseconds delay corresponding to
the new link latency, the cut off cluster starts to communicate
$\alpha$ messages again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic (only $2$
messages total), for \processes already know their closest source
located in their respective cluster.

\noindent Overall, this experimentation empirically demonstrates the
benefits of \NAME in the context of Edge infrastructures:
inter-connected autonomous systems where \processes may join or leave
or crash, communications links may be added or removed. \NAME coupled
with replication strategies designed for the Edge would allow locking
down the traffic of replica indexing, while providing every \processes
with quick access to replicated content.

### 2021-04-14 input/proposal.tex
removing url and doi of biblio + writing text of second experiment

\paragraph{Space.}
Each \process needs to maintain a vector of versions the size of which
depends on the number of sources. In the worst case, the size of this
vector increases linearly with the number of distinct sources that
ever existed in the system. For the sake of last win order, \processes
can never purge this vector from any entry. \TODO{Even when the
  \process leaves the system.} Fortunately, scoped broadcast limits
message propagation to interested \processes. A \process at a side of
the system may never hear of a source at the other side of the
system. In turns, it may never have to maintain an entry for this
source. \TODO{This is application-dependent?}

@@

\paragraph{\TODO{Time.}}
In terms of processing time, whatever the operation, it increases
linearly with the number of neighbors of the \process. It scales well,
for the number of neighbors is commonly order of magnitude lower than
the number of \processes in the system. For instance, random networks
only require $O(\log(|V|))$ neighbors to work properly \REF; and
\processes in autonomous systems have in average \TODO{X} neighbors
\REF. Lines~\ref{line:notloopingA} and \ref{line:notloopingB} can
prove costly depending on the data structure encoding paths. Using
Bloom filters however, this is \TODO{efficient}: it depends on the
number of buckets, and the number of hash functions.

@@

\paragraph{\TODO{Communication.}}
In terms of number of messages required to reach optimal
partitioning. In the average-case, a \process $i$ chosen uniformly at
random among all \processes creates a logical partition. Its messages
$\alpha_i$ propagate through the network until reaching \processes that
belong to another partition closer to them. This splits partitions in
half in average. Overall, the $a^{th}$ new partition comprises
\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
\processes. This decreases every new partition until reaching $0$
\processes per new partition: even the chosen \process already belongs
to its optimal partition. The average number of messages per \process
is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
      \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
  more messages (receipt bounded by $|O|$ as well).} Deleting the
$a^{th}$ partition generates the exact same number of messages than
the $a^{th}$ partition creation. \TODO{But what about echos?} In the
worst-case, every new partition includes all but one \process belonging
to the previous partition. The total number of messages after the
$a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot a^2)$. As
for the average-case, the number of messages for the partition
deletion is identical to the number of messages of the corresponding
partition creation.

>>>>

\begin{asparadesc}
\item [Space:]

Each \process needs to maintain a vector of versions the size of which
depends on the number of sources. In the worst case, the size of this
vector increases linearly with the number of distinct sources that
ever existed in the system. For the sake of last win order, \processes
can never purge this vector from any entry. \TODO{Even when the
  \process leaves the system.} Fortunately, scoped broadcast limits
message propagation to interested \processes. A \process at a side of
the system may never hear of a source at the other side of the
system. In turns, it may never have to maintain an entry for this
source. \TODO{This is application-dependent?}

@@

\item[Time:]

In terms of processing time, whatever the operation, it increases
linearly with the number of neighbors of the \process. It scales well,
for the number of neighbors is commonly order of magnitude lower than
the number of \processes in the system. For instance, random networks
only require $O(\log(|V|))$ neighbors to work properly \REF; and
\processes in autonomous systems have in average \TODO{X} neighbors
\REF. Lines~\ref{line:notloopingA} and \ref{line:notloopingB} can
prove costly depending on the data structure encoding paths. Using
Bloom filters however, this is \TODO{efficient}: it depends on the
number of buckets, and the number of hash functions.

@@

\item[Communication:]

In terms of number of messages required to reach optimal
partitioning. In the average-case, a \process $i$ chosen uniformly at
random among all \processes creates a logical partition. Its messages
$\alpha_i$ propagate through the network until reaching \processes
that belong to another partition closer to them. This splits
partitions in half in average. Overall, the $a^{th}$ new partition
comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a
      \rfloor}})$} \processes. This decreases every new partition
until reaching $0$ \processes per new partition: even the chosen
\process already belongs to its optimal partition. The average number
of messages per \process is
\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
      \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
  more messages (receipt bounded by $|O|$ as well).} Deleting the
$a^{th}$ partition generates the exact same number of messages than
the $a^{th}$ partition creation. \TODO{But what about echos?} In the
worst-case, every new partition includes all but one \process
belonging to the previous partition. The total number of messages
after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
a^2)$. As for the average-case, the number of messages for the
partition deletion is identical to the number of messages of the
corresponding partition creation.
